---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

data_path <- "man/data/egdata.csv"
```
# abscorr

<!-- badges: start -->
<!-- badges: end -->

The goal of abscorr is to provide easy access to common ABS structures, like
the Australian and New Zealand Standard Classification of Occupations (ANZSCO) 
and the Australian Standard Classification of Education (ASCED). 

Installation and examples below.

I'll be adding commonly-used structures as I use them myself. If you'd like 
to request one, let me know via a Github issue or email at [wfmackey@gmail.com](mailto:wfmackey@gmail.com).

## Installation

You can install the current version of `abscorr` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("wfmackey/abscorr")
```
## Example

```{r example, message=FALSE}
library(tidyverse)
library(abscorr)

glimpse(anzsco)

glimpse(asced_foe)

```


These tibbles can be tweaked and joined to your existing datasets. For example,
given a dataset of Australians by four-digit field of education and age group:

```{r}

data <- read_csv(data_path)

glimpse(data)

```

We can retrieve the four-digit fields and their corresponding two-digit fields
from `abscorr::asced_foe`:

```{r}
join_foe2 <- abscorr::asced_foe %>% 
  select(foe2, foe4) %>%   # just keep the variables you want
  distinct()               # only keep unique observations

join_foe2

```

And join with our original dataset:

```{r}

data %>% 
  left_join(join_foe2)

```

Beaut. 

